---
title: "Developing Data Product - Course Project"
author: "Garold Minkin"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: ioslides_presentation
#runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Technical Summary

- This application can be used to study some violent crime statistics by individual US States
- The application is a Shiny app created in R Studio and piblished to the ShinyApps.io hosting platform in the Cloud
- Server side functionality is implemented in the server.R file
- User interface functionality is implemented in the ui.R file
- US states map with individual states coordinates are loaded from *maps* and *mapdata* packages
- Visual details are presented using *ggplot2* package
- Crime rates per US State are provided by the *USArrests* dataset which is part of the core R package *datasets*
- *stringr* package is used for some string manipulation


## Embedded Code Example

```{r, eval = FALSE, message = FALSE}
library(ggplot2)
library(stringr)
library(datasets)
library(maps)
library(mapdata)
 
states <- map_data("state")

# Capitalize 1st letter
states$region <- str_to_title(states$region)
state_choices <- unique(states$region)

ggplot(data = states) + 
     geom_polygon(aes(x = long, y = lat, group = group), fill = "white", color = "blue")
```

## Code Execution

```{r, echo = FALSE, message = FALSE}
library(ggplot2)
library(stringr)
library(datasets)
library(maps)
library(mapdata)
 
states <- map_data("state")

# Capitalize 1st letter
states$region <- str_to_title(states$region)
state_choices <- unique(states$region)

ggplot(data = states) + 
     geom_polygon(aes(x = long, y = lat, group = group), 
                  fill = "white", color = "blue")
```

## Links to the Application and Source Code

- Application can be accessed at the URL: 
  https://garoldminkin.shinyapps.io/mapUSA/  
- Github Repository URL:  
  https://github.com/garoldminkin/DDP

